### 2021-07-21 paper.tex
added table of content, and some other corrections

\documentclass[10pt,a4paper]{article}

\usepackage{tgpagella}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=3cm]{geometry}

@@

			\vspace*{1cm}

@@

			\Large
			Department of Computer Science\\
			Gurudas College\\
			Calcutta University\\
			\today

@@

			\vspace{1cm}
			Submitted in partial fulfillment for the requirements for the
			degree of Bachelor of Science (Honors)

			\Large
			Academic Year: \textbf{2018-2021}

@@

			% supervisor
			\vspace{0.5cm}
			\rule{5cm}{0.4pt}

@@

	% certificate page
	\section*{\hfil \Huge Certificate\hfil}

@@

\end{document}

>>>>

\documentclass[12pt]{article}

\usepackage{tgpagella}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=3cm]{geometry}

% sections on new page
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}
\setcounter{secnumdepth}{0}

% index and clickable toc
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

% table of content name
\addto\captionsenglish{% Replace "english" with the language you use
	\renewcommand{\contentsname}%
	{\hfill \Huge Table of Content \hfill}%
}

@@

			\vspace*{0.5cm}

@@

			\normalsize
			Department of Computer Science\\
			Gurudas College\\
			Calcutta University\\
			\today

@@

			\normalsize
			Submitted in partial fulfillment for the requirements for the
			degree Bachelor of Science (Honors) in Computer Science.

			Academic Year: \textbf{2018-2021}

@@

			% supervisor
			\vspace{1cm}
			\rule{5cm}{0.4pt}

@@

	% certificate page
	\section[certificate]{\hfill \Huge Certificate \hfill}
	\thispagestyle{empty}

	\pagenumbering{roman}

@@

	\section[acknowledgement]{\hfill \Huge Acknowledgement \hfill}
	\label{sec:Acknowledgement}

	I would like to express my special thanks of gratitude to our supervisor
	\textbf{Kajari Bhattacharjeee}, teachers of our department \textbf{Sonali
	Gupta} and department head \textbf{Srijeeta Charkraborty}; as well as our
	principal ma'am \textbf{Dr. Mausumi Chatterjee} who gave us the golden
	opportunity to do this wonderful project on \textit{Brain tumor detection},
	which has also helped us in doing a lot of research and we came to know
	about many new things.

	We are really thankful to them.

	Secondly we would like to thank the incredible authors of the research
	papers in our references/citations for providing us with the information.

	\tableofcontents

	\section[abstract]{\hfill \Huge Abstract \hfill}

	This is going to be fun.
\end{document}
